Galaxy image statistical generator: how to be confident?

### 2024-09-03 paper/main.tex
more on intro

\cite{kadkhodaie2024generalization} address more mathematically oriented questions and demonstrate the passage between memorization to generalization of  diffusion generative models when the dataset size increases. The authors uses \textit{denoiser} architectures as \texttt{UNet} \citep{2015arXiv150504597R} and \textt{BF-CNN} networks \citep{Mohan2020Robust} trained \texttt{CelebA} \citep{Liu2015} and \texttt{LSUN} bedroom  \citep{Yu2015} reduced datasets of $O(10^5)$ images resized to $80\times 80$ pixels (grayscale). The method and image dataset characteristics are the starting point to investigate how the \texttt{Glow} normalizing flow based model compare to denoiser based diffusion model.

In the following sections, first we briefly describe the different kind of generative models and we show the outcome of the conducted numerical experiment before drawing some guide lines.

>>>>

\cite{kadkhodaie2024generalization} address more mathematically oriented questions and demonstrate the passage between memorization to generalization of  diffusion generative models when the dataset size increases and propose interpretation of what is learned by the network as a sort of \textit{geometry-adaptive harmonic basis} going beyond the commonly used \textit{steerable wavelet basis} first introduced and studied in \cite{Simoncelli1995b,Unser2013} and developped for instance in the \texttt{Kyamato} library \citep{JMLR:v21:19-047}. The authors uses \textit{denoiser} architectures as \texttt{UNet} \citep{2015arXiv150504597R} and \texttt{BF-CNN} networks \citep{Mohan2020Robust} trained on \texttt{CelebA} \citep{Liu2015} and \texttt{LSUN} bedroom  \citep{Yu2015} reduced datasets of $O(10^5)$ images resized to $80\times 80$ pixels (grayscale). The method and image dataset characteristics are the starting point to investigate how the \texttt{Glow} normalizing flow based model compare to denoiser based diffusion model concerning the generation of galaxy images both trained with the same dataset issued from SDSS suvey.

In the following sections, first we briefly describe the different kind of generative models and we show the outcome of the conducted numerical experiment before drawing some guide lines. Appendix gives more details on the dataset used.
